---
title: "R Code Chunks"
output: powerpoint_presentation
---

```{r, include=FALSE}
if (is.null(webshot:::find_phantom())) webshot::install_phantomjs()
```

### Overview

* R Code Chunks can be used as a means to render R output into documents or to simply display code for illustration. 
* You may choose to remove source code from your PowerPoint presentation by setting `echo=FALSE` in the code chunk options.

### Syntax Highlighting

Source code will render with syntax highlighting inline with other markdown text in your document. 

```{r, eval=FALSE}
library(dplyr)
nycflights13::flights %>%
  select(carrier, arr_time) %>%
  filter(!is.na(arr_time)) %>%
  group_by(carrier) %>%
  summarize(average = mean(arr_time)) %>%
  arrange(average)
````

### Table Output

Table output from `kable` will assume the table design of whatever template you use.

```{r, eval=FALSE}
knitr::kable(mtcars)
```

### Table Example

```{r, echo=FALSE}
knitr::kable(head(iris))
```

### Plot Output

* R code chunks can also be used to render plots.
* Images will be scaled automatically to fit the slide. 
* You can change image size with `fig.width` and `fig.height` code chunk options.

```{r, eval=FALSE}
library(ggplot2)
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(method = "loess")
```

### Plot Example

```{r echo=FALSE, fig.cap="Highway miles per gallon vs engine displacement"}
library(ggplot2)
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point(mapping = aes(color = class)) + 
  geom_smooth(method = "loess")
```

### Webshot

* You can capture HTML Widgets and Shiny apps by installing the `webshot` package and `phantomjs`. 
* The `webshot` package will automatically take a screenshot of an interactive HTML Widget and insert it into your presentation. 
* The `knitr::include_app` function will use webshot to embed a screenshot of a Shiny application that links viewers to a live application hosted on RStudio Connect, Shiny Server, or Shinyapps.io.

### Webshot Examples

```{r, eval=FALSE}
# Install
install.packages("webshot")
webshot::install_phantomjs()

# Capture an HTML Widget
dygraphs::dygraph(nhtemp, main = "New Haven Temperatures")

# Capture a Shiny app
knitr::include_app('https://gallery.shinyapps.io/goog-trend-index/')
```

### HTML Widget Webshot

```{r echo=FALSE, fig.cap="Screenshot of interactive dygraph"}
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))
```

### Shiny App Webshot 

```{r cache=TRUE, screenshot.opts=list(delay=5), echo=FALSE, fig.cap="Click image to open"}
knitr::include_app('https://gallery.shinyapps.io/goog-trend-index/')
```

### Useful Code Chunk Options

* Remove source code
    * `echo=TRUE`
* Cache your screenshots
    * `cache=TRUE`
* Wait for the image to load before taking a screenshot
    * `screenshot.opts=list(delay=5)`
* Specify image width or height
    * `fig.width=15`
* Add an image caption
    * `fig.cap="Click Image to Open App"`

### Code Chunk Example

In this example the code chunk will wait one second for an app to load, resize the width to 15 inches, and cache the image for later use.

```

{r, cache=TRUE, screenshot.opts=list(delay=1), fig.width=15}
```