---
title: "Bank Marketing Exploratory Analysis"
output: powerpoint_presentation
date: "`r format(Sys.time(), '%d %B, %Y')`"
---

```{r setup, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(stringr)
library(ggplot2)
library(dygraphs)
library(xts)
```

# Background

## Data source

We are working with a dataset from a Portuguese bank.  The data categorizes direct marketing efforts (phone calls) designed to sell term deposit products.  The [dataset](https://archive.ics.uci.edu/ml/datasets/Bank+Marketing) was donated to UCI's Machine Learning Repository. The goal is to predict which clients are most likely to subscribe to a term deposit. Data range from May 2008 to November 2010


```{r download, message=FALSE, eval=FALSE}
download.file(url = "https://archive.ics.uci.edu/ml/machine-learning-databases/00222/bank-additional.zip",
              destfile = "data/bank-additional.zip")

unzip(zipfile = "data/bank-additional.zip", 
      exdir = "data", 
      files = "bank-additional/bank-additional-full.csv", 
      junkpaths = TRUE)
```

## Model data set

Read data and clean up column names. Remove unnecessary columns and records. Impute year and create a column for date.

```{r model, message=FALSE, eval=FALSE}
raw_data <- read_delim(file = "data/bank-additional-full.csv",
                       delim = ";",
                       col_types = cols(nr.employed = col_number()),
                       progress = FALSE)

# Format column names
names(raw_data) <- str_replace_all(names(raw_data), "[.]", "_")

# Rename and remove columns
all_data <- raw_data %>%
    rename(term_deposit = y,
           prior_outcome = poutcome,
           personal_loan = loan,
           housing_loan = housing,
           in_default = default) %>%
  mutate(job = str_replace_all(job, "[.-]", "")) %>%
  # There's something weird with campaign... there is very spotty coverage after 35 (up to 56).
  mutate(campaign = pmin(campaign, 35)) %>%
  mutate(total_contacts = campaign + previous) %>%
  select(-c(nr_employed, emp_var_rate, previous, pdays, campaign, duration)) %>%
  na.omit

# Impute year and date
all_data <- all_data %>%
  mutate(month_idx = ifelse(month != lag(month, default = "may"), 1, 0)) %>%
  mutate(month_idx = cumsum(month_idx)) %>%
  mutate(year = findInterval(month_idx, c(7, 17))) %>%
  mutate(year = case_when(year == 0 ~ "2008",
                          year == 1 ~ "2009",
                          year == 2 ~ "2010")) %>%
  mutate(date = as.Date(paste0("1", month, year), "%d%b%Y"))

saveRDS(all_data, file = "data/all_data.RDS")
```

# Exploratory data analysis

```{r alldata}
all_data <- readRDS('data/all_data.RDS')

# Monthly rollup
dat <- all_data %>%
  group_by(month_idx, year, month, date) %>%
  summarize(subscribe = sum(term_deposit == "yes"), 
            total = n(),
            percent = 100 * mean(term_deposit == "yes"))
```

## Total contacts and subscriptions

```{r contacts, fig.cap="There were far more contacts in 2008 and 2009."}
# Totals
with(dat, xts(cbind(Total = total, Subscribe = subscribe), date)) %>%
  dygraph(main = "Total contacts and subscriptions") %>%
  dyRangeSelector()
```

```{r econ}
p <- all_data %>%
  group_by(month_idx, year, month) %>%
  summarize(euribor3m = mean(euribor3m),
            cons_conf_idx = mean(cons_conf_idx),
            cons_price_idx = mean(cons_price_idx),
            term_deposit = 100 * mean(term_deposit == "yes")) %>%
  ungroup %>%
  mutate_at(vars(euribor3m, cons_conf_idx, cons_price_idx),
                 function(x) (x - min(x)) / (max(x) - min(x))) %>%
  gather("key", "value", euribor3m, cons_conf_idx, cons_price_idx)
```

## Economic indicators

```{r indicators, fig.cap="Term deposits are correlated to some extent with macro economic indicators."}
ggplot(p, aes(month_idx, value, color = key)) +
  geom_line() +
  ggtitle("Economic Indicators") +
  xlab("Month") +
  ylab("Index")
```

## Term deposit percent

```{r deposit, fig.cap="Lower rates of `euribor3m` were associated with associated with more term desposits."}
ggplot(p, aes(term_deposit, value, color = year)) +
  geom_point() +
  facet_grid(~key) +
  ggtitle("Economic Indicators vs Term Deposits") +
  xlab("Term Deposit Percent") +
  ylab("Index")
```

## Term deposits

```{r euribor3m, fig.cap="Clients with a successful prior outcome were much more likley to subscribe to a term deposit."}
ggplot(all_data, aes(euribor3m, color = term_deposit)) +
  geom_density(adjust=0.05) +
  ggtitle("Term deposits")
```

## Prior outcome

```{r, priors}
all_data %>%
  group_by(term_deposit) %>%
  count(prior_outcome) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  select(-n) %>%
  spread(term_deposit, pct) %>%
  knitr::kable(.)
```

## Term deposit by age

```{r age, fig.cap="Contacts who subscribe to term deposits skew slightly older and younger."}
qplot(term_deposit, age, data = all_data, geom = "boxplot") +
  ggtitle("Term deposit by age")
```

## Term deposits by month

```{r monthly, fig.cap="October saw an unusually high percent of term deposits in 2008."}
all_data %>%
  group_by(year, month) %>%
  summarize(term_deposit = 100 * mean(term_deposit == "yes")) %>%
  ggplot(aes(month, term_deposit, fill = year)) +
  geom_bar(stat = "identity", position="stack") +
  ggtitle("Monthly term deposits")
```

## Jobs by subscription

```{r jobs}
all_data %>%
  group_by(term_deposit) %>%
  count(job) %>%
  mutate(pct = round(100 * n / sum(n), 1)) %>%
  select(-n) %>%
  spread(term_deposit, pct) %>%
  knitr::kable(.)
```

## Contact volume

```{r volume, fig.cap="There were far more contacts in 2008 than in 2010"}
all_data %>%
  group_by(year, month) %>%
  summarize(term_deposit = sum(term_deposit == "yes"), count = n()) %>%
  ggplot(aes(count, term_deposit, color = year)) +
  geom_point() +
  xlab("Total contacts") +
  ylab("Term Deposit Subscriptions") +
  ggtitle("Contact volume")
```

# Summary

## Conclusions

There is a lot of variability in total contacts and in percentage of term deposit subscriptions over time. There were far more contacts made in 2008 when the three month Euribor rate was high. As total contacts dropped, the percentage of term deposit subscriptions increased.

Subscriptions are correlated with a variety of factors, including age and job to name a few. There is also a strong correlation with prior outcomes, as one might expect.

## Next steps

:::::::::::::: {.columns}
::: {.column}
This analysis only analyzed a few select variables. The next goal should be to predict term deposit subscriptions as a function of all the variables in the data.
:::
::: {.column}
Use the following models to predict term deposit and compare model performance: 

* Logistic
* Ranger
* with cross validation (Caret)
:::
::::::::::::::

