---
title: "Stock Report"
subtitle: "Summary"
output:
  powerpoint_presentation:
#    reference_doc: rstudio-template.pptx
params:
  symbol: TSLA
  start:
    label: "Start:"
    value: !r Sys.Date() - 21
    input: date
  end:
    label: "End:"
    value: !r Sys.Date()
    input: date
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyquant)
dat <- tq_get(params$symbol, get = "stock.prices", from = params$start, to = params$end)
curr <- dat %>% mutate_all(round, 2) %>% tail(1)
```

# `r params$symbol`: `r params$start` to `r params$end`

### Summary

`r params$symbol` closed `r ifelse(curr$close > curr$open, "up", "down")` at `r curr$close` dollars per share on `r params$end`.

* High: `r curr$high`
* Low: `r curr$low`
* Close: `r curr$close`

::: notes
Data were analyzed using these packages:

* tidyquant
* quantmod
* tidyverse
:::

### Price History

```{r, fig.cap=paste("Stock prices for", params$symbol)}
dat %>%
    ggplot(aes(x = date, y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close),
                        color_up = "darkgreen", color_down = "darkred", 
                        fill_up  = "darkgreen", fill_down  = "darkred") +
    labs(title = paste(params$symbol, "Candlestick Chart"), y = "Closing Price", x = "") +
    theme_tq()
```

### `r params$symbol` last week

```{r}
dat %>%
  select(date, open, high, low, close) %>%
  tail(7) %>%
  knitr::kable(.)
```

### Volume

:::::::::::::: {.columns}
::: {.column}
`r params$symbol` trading volume was `r format(curr$volume, big.mark = ",", scientific = FALSE)` shares on `r params$end`. Average trading volume over this time period was `r format(mean(round(dat$volume)), big.mark = ",", scientific = FALSE)` shares.
:::
::: {.column}
```{r, fig.cap=paste("Trading volume for", params$symbol)}
ggplot(dat, aes(date, volume)) +
  geom_bar(stat="Identity") +
  labs(title = paste(params$symbol, "Volume"), y = "Volume", x = "") +
  theme_tq()
```
:::
::::::::::::::

