---
title: Shiny and PowerPoint
subtitle: How to include a Shiny app in your presentation
output: powerpoint_presentation
---

# Overview

What if you want to include a Shiny application in your PowerPoint presentation? With the `webshot` package, you can embed a screenshot of a Shiny application that links viewers to a live application hosted on RStudio Connect, Shiny Server, or Shinyapps.io.

# Requirements

Install the [webshots](https://cran.r-project.org/web/packages/webshot/vignettes/intro.html) package and [phantomjs](http://phantomjs.org/).

```{r, eval=FALSE}
install.packages("webshot")
webshot::install_phantomjs()
```

# Using

Use `knitr::include_app('<URL>')` to include a Shiny application in your presentation. The render process will automatically take a screenshot of your Shiny app and link the image to your hosted app.

```
knitr::include_app('https://gallery.shinyapps.io/goog-trend-index/')
```
# Useful [chunk options](https://yihui.name/knitr/options/?version=1.2.544-1&mode=server)

You can use `knitr` options to control the `webshot` experience.

* Specify image width
    * `fig.width=15`
* Cache your screenshots
    * `cache=TRUE`
* Wait for the image to load before taking a screenshot
    * `screenshot.opts=list(delay=5)`
* Add an image caption
    * `fig.cap="Click Image to Open App"`

# Include a Shiny App in PowerPoint

```{r, echo=FALSE, fig.cap="Click image to open"}
knitr::include_app('https://gallery.shinyapps.io/goog-trend-index/')
```




