---
title: "Customer Tracker Report"
output: powerpoint_presentation
date: "`r Sys.Date()`"
params:
  seg: 
    label: "Segment:"
    value: Total
    input: select
    choices: [Total, Heavy, Mainstream, Focus1, Focus2, 
              Specialty, Diverse1, Diverse2, Other, New]
  grp: 
    label: "Group:"
    value: Total
    input: select
    choices: [Total, Core, Extra]
  per: 
    label: "Period:"
    value: Week
    input: radio
    choices: [Week, YTD]
---


## Overview

Data were compared from pre and post periods by week. This report shows pecentage change by:

* `r params$seg` (segment)
* `r params$grp` (group)
* `r params$per` (period)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
library(readr)
library(tidyverse)
library(plotly)
library(openxlsx)
library(openxlsx)
library(formattable)
library(blastula)
```

```{r pulldata, cache=TRUE}
curr <- read_csv("data/trackerCalcCurr.csv")
pre <- read_csv("data/trackerCalcPre.csv")
users <- read_csv("data/users.csv")
```

```{r format}
f <- function(x, y) {(y / x - 1)}
dat <- bind_cols(
  curr %>%
    filter(segment == params$seg) %>%
    select(ends_with(paste0(params$grp, params$per))) %>%
    rename_at(1:3, ~c("purchasesCurr", "itemsCurr", "dollarsCurr")),
  pre %>%
    filter(segment == params$seg) %>%
    select(ends_with(paste0(params$grp, params$per))) %>%
    rename_at(1:3, ~c("purchasesPre", "itemsPre", "dollarsPre"))
) %>%
  mutate(
    Week = 1:52,
    RevenuePre = dollarsPre,
    RevenueCurr = dollarsCurr,
    Revenue = f(dollarsPre, dollarsCurr),
    CustomersPre = filter(users, segment == params$seg) %>% .$pre,
    CustomersCurr = filter(users, segment == params$seg) %>% .$curr,
    Customers = f(CustomersPre, CustomersCurr),
    VisitsPre = purchasesPre / CustomersPre,
    VisitsCurr = purchasesCurr / CustomersCurr,
    Visits = f(VisitsPre, VisitsCurr),
    ItemsPre = itemsPre / purchasesPre,
    ItemsCurr = itemsCurr / purchasesCurr,
    Items = f(ItemsPre, ItemsCurr),
    SpendPre = dollarsPre / itemsPre,
    SpendCurr = dollarsCurr / itemsCurr,
    Spend = f(SpendPre, SpendCurr)
  ) %>%
  filter(Week <= 22) %>%
  #arrange(desc(Week)) %>%
  select(
    Week, RevenuePre, RevenueCurr, Revenue,
    CustomersPre, CustomersCurr, Customers,
    VisitsPre, VisitsCurr, Visits,
    ItemsPre, ItemsCurr, Items,
    SpendPre, SpendCurr, Spend
  )
```

## Results

```{r plot, fig.height=7.5, fig.width=15}
pdat <- dat %>%
  select(Week, Revenue, Customers, Visits, Items, Spend) %>%
  gather(seg, metric, -Week) %>%
  mutate(metric = round(100 * metric, 2)) %>%
  mutate(seg = factor(seg, levels = c("Spend", "Items", "Visits", "Customers", "Revenue")))

p1 <- ggplot(filter(pdat, seg != "Revenue"), aes(Week, metric, fill = seg)) +
  geom_bar(stat = "Identity") + 
  geom_line(data = filter(pdat, seg == "Revenue"), aes(Week, metric), col = "darkgrey") +
  scale_fill_manual(values = alpha(c("orange", "salmon", "darkgrey", "lightgreen", "lightblue"), 0.5)) +
  labs(x = "Week", y = "Percent", title = "Percentage change by Week") +
  theme_minimal() +
  theme(legend.title=element_blank())

p1
```

## Detail

```{r data}
sign_formatter <- formatter("span", 
  style = x ~ style(color = ifelse(x > 0, "green", 
    ifelse(x < 0, "red", "black"))))

bar_formatter <- formatter("span",
  style = x ~ style(
    display = "inline-block", 
    direction = ifelse(x > 0, "rtl", "ltr"), 
    `border-radius` = "4px", 
    `padding-right` = "2px",
    `font-weight` = "bold",
    `background-color` = csscolor(ifelse(x > 0, "palegreen", "pink")), 
    width = percent(proportion(as.numeric(x)))))

tile_formatter <- formatter("span",
  style = x ~ style(
    display = "block", 
    padding = "0 4px", 
    `border-radius` = "4px",
    `color` = "grey50",
    `font-weight` = "bold",
    `background-color` = ifelse(x > 0,
                                csscolor(gradient(as.numeric(x), "white", "palegreen")),
                                csscolor(gradient(as.numeric(x), "pink", "white")))))

# Table data
t0 <- dat %>%
  select(Week, RevenuePre, RevenueCurr, Revenue, Customers, Visits, Items, Spend)

# Number formats
t1 <- t0 %>%
  mutate_at(vars(Revenue:Spend), ~ percent(.x, digits = 1)) %>%
  mutate_at(vars(RevenuePre, RevenueCurr), ~ currency(.x, digits = 0))

# HTML formats
t2 <- formattable(t1, list(
    Revenue = tile_formatter,
    Customers = sign_formatter,
    Visits = sign_formatter,
    Items = sign_formatter,
    Spend = sign_formatter
    )
)

knitr::kable(head(select(t1, -RevenuePre, -RevenueCurr), 12))
```

## Shiny App

:::::::::::::: {.columns}
::: {.column}
This report is for:

* Segment: `r params$seg`
* Group: `r params$grp`

Use the Shiny app to explore explore other segments and groups.
:::
::: {.column}
```{r webshot, cache=TRUE, screenshot.opts=list(delay=3), fig.width=15, fig.cap="Click image to open app."}
if (is.null(webshot:::find_phantom())) webshot::install_phantomjs()
knitr::include_app('http://colorado.rstudio.com/rsc/content/1120/')
```
:::
::::::::::::::

::: notes
Click on the image to open the Shiny app in RStudio Connect. Or visit online at http://colorado.rstudio.com/rsc/content/1120/.
:::

```{r download, include=FALSE}
reportLab <- "Customer Tracker Presentation"
pngfile <- paste0(reportLab, ".png")
xlsfile <- paste0(reportLab, ".xlsx")
wb <- createWorkbook()
addWorksheet(wb, "Summary", gridLines = FALSE)
ggsave(pngfile, p1, "png", width = 6, height = 3)
insertImage(wb, "Summary", file = pngfile)
writeData(wb, "Summary", t0, startRow = 16)
addWorksheet(wb, sheetName = "Data")
writeDataTable(wb, sheet = 2, dat)
saveWorkbook(wb, xlsfile, overwrite = TRUE)
```

```{r}
lab <- paste(params$seg, params$grp, params$per, sep = "-")
p2 <- add_ggplot(p1, 6, 3)

email <- compose_email("
{reportLab} for {lab} as of {add_readable_time()}.

Hightlights include **{tail(t1, 1)$Revenue} change in revenue** as a result of:

* **{tail(t1, 1)$Visits} change in visits**
* **{tail(t1, 1)$Items} change in items**
* **{tail(t1, 1)$Spend} change in spend**

{p2} \n {t2}

For specific data relevant to other segments or groups, view the report on [RStudio Connect](http://colorado.rstudio.com/rsc/connect/#/apps/1646/access/1880).
")

rmarkdown::output_metadata$set(
  rsc_email_subject = paste(reportLab, "for", lab),
  rsc_email_body_html = email$html_str,
  rsc_email_images = email$images,
  rsc_email_attachments = xlsfile
)
```
